A generalized definition of multidimensional item response theory parameters

### 2022-07-19 output/paper_draft/paper_M2PLM_parameters.Rmd
Drops person index "j" from the whole notation

Consider a $`r N_DIMS`$-dimensional latent space $`r LATENT_SPACE`$,
defined by vector space $V$ and basis $`r LS_BASIS`$,
being $`r LS_BASIS_EQ`$ an arbitrary set of linearly independent vectors.
Person $j$ is represented in $`r LATENT_SPACE`$ by vector
$`r TRAIT_VC_PERSON_J`$,
being $`r TRAIT_VECTOR`$ a multivariate normal variable

@@

being  
$`r IRF_M2PL`$ ($= `r IRF_ABBR`$ henceforth, for simplicity) the probability of
a positive response to item $`r ITEM_INDEX`$ by person $`r PERSON_INDEX`$,  
$`r DISCR_VECTOR`$ a $`r N_DIMS`$-dimensional vector of
discrimination parameters, and  
$`r INTERCEPT_PARAM`$ an intercept parameter related to the location of the item
in the latent space.

@@

Following the procedure outlined by @reckase_difficulty_1985
[@reckase_discriminating_1991],
we first compute the point of maximum slope by finding the root(s) of
the second derivative with respect to $`r TRAIT_J_MODULE`$.

@@

The root we are interested in is found for $`r IRF_MAX_SLOPE_EQ`$
(the other ones occur when $`r IRF_ABBR`$ equals 0 and 1,
which result in improper values of $`r TRAIT_J_MODULE`$).
The slope in direction $`r DIR_ANGLE_J_VEC`$ is given by

>>>>

Consider a $`r N_DIMS`$-dimensional latent space $`r LATENT_SPACE`$,
defined by vector space $V$ and basis $`r LS_BASIS`$,
being $`r LS_BASIS_EQ`$ an arbitrary set of linearly independent vectors.
A respondent is represented in $`r LATENT_SPACE`$ by
coordinate vector $`r TRAIT_VECTOR`$, assumed to be multivariate normal:

@@

being  
$`r IRF_M2PL`$ ($= `r IRF_ABBR`$ henceforth, for simplicity) the probability of
a positive response to item $`r ITEM_INDEX`$ for a given $`r TRAIT_VECTOR`$,  
$`r DISCR_VECTOR`$ a $`r N_DIMS`$-dimensional vector of
discrimination parameters, and  
$`r INTERCEPT_PARAM`$ an intercept parameter related to the location of the item
in the latent space.

@@

Following the procedure outlined by @reckase_difficulty_1985
[@reckase_discriminating_1991],
we first compute the point of maximum slope by finding the root(s) of
the second derivative with respect to $`r TRAIT_VECTOR`$.

@@

The root we are interested in is found for $`r IRF_MAX_SLOPE_EQ`$
(the other ones occur when $`r IRF_ABBR`$ equals 0 and 1,
which result in improper values of $`r TRAIT_MODULE`$).
The slope in direction $`r DIR_ANGLE_VEC`$ is given by
